Case study: Genome-Wide Association Analyses (GWAS)

### 2018-03-22 datasets/GWAS/GWAS.Rmd
Fix pk typos in plink system call

```{r, clump}
## use PLINK clumping tool to obtain a set of independent SNPs by LD
if (!dir.exists(plink_clump)) {
    system(paste("plink",
                 "--bfile DATA/1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01",
                 "--clump DATA/rslist.assoc",
                 "--clump-field P",
                 "--clump-p1 0.9999",
                 "--clump-p2 0.9999",
                 "--clump-r2 0.2",
                 "--clump-kb 250",
                 "--out DATA/plink_clump"))
}
```

>>>>

```{r, clump}
## use PLINK clumping tool to obtain a set of independent SNPs by LD
if (!file.exists(file.path(datdir, "plink_clump.clumped"))) {
    code <- paste("plink",
                  "--bfile", file.path(datdir, "1000G_20101123_v3_GIANT_chr1_23_minimacnamesifnotRS_CEU_MAF0.01"),
                  "--clump", file.path(datdir, "rslist.assoc"),
                  "--clump-field P",
                  "--clump-p1 0.9999",
                  "--clump-p2 0.9999",
                  "--clump-r2 0.2",
                  "--clump-kb 250",
                  "--out", file.path(datdir, "plink_clump"))
    system(code)
}
```
